### 2017-03-06 README.Rmd
updated README and docs

# ggplot2 version
library(ggplot2)
p2 <- autoplot(pd, contour = TRUE, title = "ggplot2 version", 
               legend.title = "Partial\ndependence")

@@

# Show both plots in one figure
grid.arrange(autoplot(pd.glucose, title = "Logit scale"), 
             autoplot(pd.glucose.prob, title = "Probability scale"), 
             ncol = 2)
```

>>>>

# ggplot2 version
library(ggplot2)
p2 <- autoplot(pd, contour = TRUE, main = "ggplot2 version", 
               legend.title = "Partial\ndependence")

@@

# Show both plots in one figure
grid.arrange(autoplot(pd.glucose, main = "Logit scale"), 
             autoplot(pd.glucose.prob, main = "Probability scale"), 
             ncol = 2)
```
